---
title: "BKM Assignment"
author: "Tunahan Kılıç"
date: "11 Kasım 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
# 1.BKM Dataset

BKM data includes the numerical values for transactions made from credit card and debit card, including the number of transactions and transaction amount according to sectoral groups. The analysis was conducted using data from the beginning of 2017 to the period of June 2019.


## 2.Preparing and Cleaning Dataset

### 2.1. Preparing Dataset

Loading required libraries for analysis
```{r pressure, warning=FALSE, message=FALSE}
library(rvest)
library(tidyverse)
library(lubridate)
library(ggplot2)
```


```{r get_df, warning=FALSE, message=FALSE}
getYearMonth<- function(year,month) {
  url <- paste('https://bkm.com.tr/secilen-aya-ait-sektorel-gelisim/?filter_year=',year,'&filter_month=',month,'&List=Listele', sep='',collapse = NULL)
  return(url)
}

bkm_year <-c('2017','2018','2019')
bkm_month <- c('01','02','03','04','05','06','07','08','09','10','11','12')
bkm_full <- ""

for (i in 1:length(bkm_year)) {
  for (j in 1:length(bkm_month)) {
    if (bkm_year[i] == "2019" & bkm_month[j] == "07") {break}
    url<-getYearMonth(bkm_year[i],bkm_month[j])
    pages <- read_html(url)
    df <- pages %>% html_nodes("table") %>% .[(4)] %>% html_table(pages, fill = TRUE, header = FALSE)  %>%  as.data.frame() %>% slice(3:max(nrow(.)))  
    df <- df %>% mutate_if(is.numeric,funs(ifelse(is.na(.),0,.))) %>%  mutate(yearMonth = paste(bkm_year[i],bkm_month[j],sep='-'))
    bkm_full <- rbind(bkm_full, df)
  }
}

colnames(bkm_full) <- c("isyeri_grubu", "kk_islem_adedi", "bk_islem_adedi", "kk_islem_tutari", "bk_islem_tutari", "yil_ay")
```

### 2.2. Cleaning Dataset
```{r clean_df, warning=FALSE, message=FALSE}
options(scipen = 999)

#Removing "TOPLAM" rows that belongs to each month
bkm_full <- bkm_full %>% filter(!str_detect(isyeri_grubu,"TOPLAM"))

#Converting char yil_ay column to date format
bkm_full$yil_ay <- lubridate::ymd(bkm_full$yil_ay, truncated = 1L)
bkm_full = bkm_full[-1,]


head(bkm_full)

str(bkm_full)
```

```{r change_to_num, warning=FALSE, message=FALSE}
#Creating year column in a df
bkm_full$yil <- year(ymd(bkm_full$yil_ay))


#Changing chars to numeric value
bkm_full$kk_islem_adedi <- as.numeric(str_replace_all(bkm_full$kk_islem_adedi, pattern=fixed("."), ""))
bkm_full$bk_islem_adedi<-as.numeric(str_replace_all(bkm_full$bk_islem_adedi, pattern=fixed("."), ""))

#Replacing thousand separator with " " and decimal separator "," with "."
bkm_full$kk_islem_tutari<-str_replace_all(bkm_full$kk_islem_tutari, pattern=fixed("."), "")
bkm_full$kk_islem_tutari<-as.numeric(str_replace_all(bkm_full$kk_islem_tutari, pattern=fixed(","), "."))

bkm_full$bk_islem_tutari<-str_replace_all(bkm_full$bk_islem_tutari, pattern=fixed("."), "")
bkm_full$bk_islem_tutari<-as.numeric(str_replace_all(bkm_full$bk_islem_tutari, pattern=fixed(","), "."))
```

## 3.Exploratory Data Analysis for BKM Dataset

### 3.1.Top 3 Monthly Card Transaction Amounts in Total
```{r toplam_islem, warning=FALSE, message=FALSE}
top_sales_bkm <- bkm_full %>% group_by(yil_ay, isyeri_grubu) %>% summarise(islem_tutari = sum(kk_islem_tutari) + sum(bk_islem_tutari)) %>% top_n(3)
top_sales_bkm
ggplot(top_sales_bkm, aes(x = ordered(yil_ay), y = islem_tutari, fill = isyeri_grubu)) + geom_bar(stat = "identity") + 
  theme(axis.text.x = element_text(angle = 90, hjust = 1)) + 
  labs(x = "Aylık Dönemler", y = "Toplam İşlem Tutarı (KK+BK)", fill = "Isyeri Grubu")
```

### 3.2.Ratio of Debit Card Transactions in Total Card Transactions
```{r debit_ratio, warning=FALSE, message=FALSE}

bkm_debit_ratio <- bkm_full %>% group_by(yil, isyeri_grubu) %>% summarise(toplam_islem_bk = sum(bk_islem_adedi), toplam_kart_islem = sum(bk_islem_adedi) + sum(kk_islem_adedi), ratio_bk = toplam_islem_bk/toplam_kart_islem) %>% top_n(5) %>% arrange(desc(ratio_bk))
bkm_debit_ratio

#Required libraries for animated plots
library(gganimate)
library(gifski)
library(png)
theme_set(theme_bw())

p <- ggplot(bkm_debit_ratio, aes(x = yil, y = ratio_bk, group = isyeri_grubu, color = isyeri_grubu)) + geom_line() +
  scale_x_continuous(breaks = 0:2100) +
  labs(x = "Yıl", y = "Banka Kartı Kullanım Oranı", color = "Isyeri Grubu") +
  theme(legend.position = "right")
p + geom_point(aes(group = seq_along(yil))) + transition_reveal(yil) #Animated debit card ratio plot
```
