---
title: "ATP Tennis Dataset Analysis"
author: "Tunahan Kılıç"
date: "December 1st, 2019"
output: 
  html_document:
    toc: true
    toc_float: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Library Import
```{r message=FALSE, warning=FALSE}
library(tidyverse)
```

## Exploring Data Frames 
```{r message=FALSE, warning=FALSE}
atp_data <- load("atp_tennis_data_2017.RData")

str(tourney_df)
str(player_df)
str(rank_df)
str(score_df)
str(stats_df)
```

## 1. Rank Countries (Flag Codes) by the Singles Champions
```{r}

champs_flags <- tourney_df %>% left_join(player_df, by = c("singles_winner_player_id" = "player_id")) %>% group_by(flag_code) %>% count(flag_code, sort = TRUE)

champs_flags
```


## 2. Rank countries which did not get any singles champs by the games won when they win the match
```{r}
player_df %>% select(player_id, flag_code) %>% anti_join(.,champs_flags) %>% 
  left_join(score_df, by = c("player_id" = "winner_player_id")) %>% 
  group_by(flag_code) %>% summarise(total_wins = sum(winner_games_won, na.rm = TRUE)) %>% arrange(desc(total_wins))
```


## 3. Rank Countries (Flag Codes) by the Double Champs
```{r}
double_winners <- tourney_df %>% 
  left_join(player_df, by = c("doubles_winner_1_player_id" = "player_id", "doubles_winner_2_player_id" = "player_id")) %>%
  select(tourney_name, flag_code, doubles_winner_1_player_id, doubles_winner_2_player_id)

double_winners
```

### 3.1. Checking All Double Pairs are from the same countries
```{r}
double_winners %>% gather("Winner_Player_IDs", "IDs", doubles_winner_1_player_id:doubles_winner_2_player_id)

double_winners %>% group_by(flag_code) %>% count(flag_code, sort = TRUE)
```



## 4. Total Aces by Each Player in 2017
```{r}
score_df$tourney_id <- as.numeric(score_df$tourney_id)
stats_df$tourney_id <- as.numeric(stats_df$tourney_id)
```

### 4.1. Total Aces of Winners
```{r}
winner_aces_total <- stats_df %>% 
  left_join(player_df, by = c("winner_player_id" = "player_id")) %>%
  select(winner_player_id, first_name, last_name, winner_aces) %>%
  mutate(full_name = paste(first_name, last_name)) %>%
  group_by(full_name) %>%
  summarise(winner_total_aces = sum(winner_aces)) %>% select(full_name, winner_total_aces) %>% arrange(desc(winner_total_aces))

winner_aces_total
```

### 4.2. Total Aces of Losers
```{r}
loser_aces_total <- stats_df %>% 
  left_join(player_df, by = c("loser_player_id" = "player_id")) %>%
  select(loser_player_id, first_name, last_name, loser_aces) %>%
  mutate(full_name = paste(first_name, last_name)) %>%
  group_by(full_name) %>%
  summarise(loser_total_aces = sum(loser_aces)) %>% select(full_name, loser_total_aces) %>% arrange(desc(loser_total_aces))

loser_aces_total
```

### 4.3. Total Number of Aces by Players
```{r}
total_aces_full <- winner_aces_total %>% left_join(loser_aces_total, by = "full_name") %>% mutate(aces_total = winner_total_aces + loser_total_aces) %>% arrange(desc(aces_total))

#Removing the row that is shown with full name "NA NA"
total_aces_full <- subset(total_aces_full, full_name != "NA NA")

head(total_aces_full, 10)
```
